Gravitational wave sources in our Galactic backyard: Predictions for BH and NS binaries in LISA

### 2021-06-18 paper/tex/sections/results.tex
add commands make things consistent, update table

In this section we present our main results for the detectable LISA DCO population. We find that, for our fiducial model, a four 4-year LISA mission will detect \confinv{30.6}{20.5}{51.1} BHBHs, \confinv{26.4}{17.3}{48.5} BHNSs and \confinv{7.1}{4.8}{10.8} NSNSs where the error bars represent the 90\% confidence interval. We first show the distribution of the sources on the sensitivity curve in Section~\ref{sec:dcos_on_sc}, before exploring the variations in the detection rate over different physics variations in Section~\ref{sec:detection_rate_analysis} and analysing the parameter distributions for detectable sources in the fiducial model in Section~\ref{sec:fiducial_distributions}.

@@

\subsection{Detection rates}\label{sec:detection_rate_analysis}
\todo{I will be updating this section once the other physics variations are done running. There will be a couple of new models and the current ones will have better high Z resolution.}
We find that for our fiducial model, a 4-year LISA mission will detect \confinv{30.6}{20.5}{51.1} BHBHs, \confinv{26.4}{17.3}{48.5} BHNSs and \confinv{7.1}{4.8}{10.8} NSNSs, where the error bars represent the 90\% confidence interval. Increasing to a 10-year LISA mission length changes the number of detections to \confinv{50.6}{29.2}{63.3}, \confinv{46.2}{25.7}{99.3} and \confinv{12.1}{6.9}{13.5} respectively. In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections for each model variation and discuss the prominent trends in the following sections. We show the rates and uncertainties plotted in this figure in Table~\ref{tab:detection_rates}.

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{3_dco_detections.pdf}
    \caption{The number of expected detections in the LISA mission for different DCO types and model variations. Error bars show the 50\% (solid) and 90\% (dotted) confidence intervals. The left axis and grid lines show the number of detections in a 4-year LISA mission and the right axis shows an approximation of the number of detections in a 10-year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates). Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{sec:fiducial_physics}. \todo{subject to change with the updated/new models}}
    \label{fig:detection_rates}
\end{figure*}

>>>>

In this section we present our main results for the detectable LISA DCO population. We find that on average, for our fiducial model, a 4-year LISA mission will detect \BHBHFourYear{} BHBHs, \BHNSFourYear{} BHNSs and \NSNSFourYear{} NSNSs. We first show the distribution of the sources on the sensitivity curve in Section~\ref{sec:dcos_on_sc}, before exploring the variations in the detection rate over different physics variations in Section~\ref{sec:detection_rate_analysis} and analysing the parameter distributions for detectable sources in the fiducial model in Section~\ref{sec:fiducial_distributions}.

@@

\subsection{Detection rates}\label{sec:detection_rate_analysis}
\todo{I will be updating this section once the other physics variations are done running. There will be a couple of new models and the current ones will have better high Z resolution.}
We find that for our fiducial model on average, a 4-year LISA mission will detect \BHBHFourYear{} BHBHs, \BHNSFourYear{} BHNSs and \NSNSFourYear{} NSNSs. Increasing to a 10-year LISA mission length changes the number of detections to \BHBHTenYear{}, \BHNSTenYear{} and \NSNSTenYear{} respectively. In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections for each model variation and discuss the prominent trends in the following sections. We show the rates and uncertainties plotted in this figure in Table~\ref{tab:detection_rates}.

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{3_dco_detections.pdf}
    \caption{The number of expected detections in the LISA mission for different DCO types and model variations. Error bars show the 50\% (solid) and 90\% (dotted) confidence intervals. The left axis and grid lines show the number of detections in a 4-year LISA mission and the right axis shows an approximation of the number of detections in a 10-year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates). Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{sec:fiducial_physics}. \todo{subject to change with the updated/new models and new uncertainty estimates}}
    \label{fig:detection_rates}
\end{figure*}
